%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Audio Signal Processing Engineer} % Job title
    {Chowdhury DSP} % Organization
    {Denver, C0} % Location
    {Oct. 2021 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed signal processing algorithms for real-time audio processing and synthesis.}
        \item {DSP algorithms include: virtual analog modelling, machine learning, and frequency-domain processing.}
        \item {Developed audio plugins including DSP, UI implementation, preset management, copy protection, installers, etc.}
        \item {Contributed to open-source audio plugins and signal processing libraries.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audio Test Engineer} % Job title
    {Tesla Motors} % Organization
    {Palo Alto, CA} % Location
    {Aug. 2020 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed audio system signal flow layouts for vehicles using AudioWeaver.}
        \item {Contributed to audio system testing and tuning including telephony, equalization, and spatialization.}
        \item {Developed end-of-line tests to ensure vehicle audio system quality using Python and C++.}
        \item {Contributed to the signal processing and tuning for the vehicle pedestrian warning speaker.}
        \item {Contributed to testing and validation software for audio system firmware.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software/DSP Engineer} % Job title
    {Persp3ctive VR} % Organization
    {Los Angeles, CA} % Location
    {June 2019 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and implemented audio effects for use in a VR audio production environment including:}
        \begin{itemize}
            \item {Parametric EQ, with smoothly varying parameters and five filter types.}
            \item {Dynamic range compression, with virtual analog models of
                   an optical compressor, and output transformer.}
        \end{itemize}
        \item {Implemented the audio effects as an audio plugin with a fully featured UI.}
        \item {Built DSP framework for integrating effects made by other engineers into the plugin.}
        \item {Implemented OSC communication for sharing parameters and metering data with VR headset.}
        \item {Developed unit testing framework to make overall software more robust.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Audioworks Technologies} % Organization
    {Toronto, ON} % Location
    {July 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of of the SoundsUnite developement team: building a digital audioworkstation (DAW) using JUCE/C++.}
        \item {Developed DSP features for the application including panning algorithms, level detection, and ``smart'' track exporting.}
        \item {Developed UX features for the application including meters, file browsers, and tempo controls.}
        \item {Integrating the application file management system with the SoundsUnite web store.}
        % \item {Presented work to engineering team, managers, and investors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Trainee} % Job title
    {McGill Space Institute} % Organization
    {Montreal, QC} % Location
    {May 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recipient of an Undergraduate Student Research Award from the National Sciences and Engineering Research Council of Canada.}
        \item {Member of the CHIME/FRB Working Group: building a software pipeline to detect Fast Radio Bursts (FRBs).}
        \item {CHIME is a telescope in British Columbia; has detected more FRBs in the Northern Hemisphere than any other telescope to date.}
        \item {Developed a ``Flux Estimator'' module for the CHIME/FRB software pipeline: Use incoming data from the telescope to estimate the intrinsic brightnes of the astrophsyical source.}
        \item {Contributed to science and unit testing frameworks for the CHIME/FRB software pipeline.}
        \item {Presented work for CHIME/FRB Working Group and CHIME/FRB Pipeline Gamma Release.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Tutor} % Job title
    {USC Viterbi Academic Resources Center} % Organization
    {Los Angeles, CA} % Location
    {Aug. 2018 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored undergraduate engineering students in math, physics, and electrical engineering classes.}
        \item {Served as a tutor for the university chapter of the Society of Hispanic Professional Engineers.}
        \item {Trained new tutors in interacting with students and presenting material in a clear, concise, and cohesive manner.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Disc Jockey, Jazz Director} % Job title
    {KXSC Radio} % Organization
    {Los Angeles, CA} % Location
    {Jan. 2015 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {On-air host and disc jockey for live jazz radio program ``Jam Sessions''.}
        \item {Co-host of live radio talk-show programs ``Squaminous Science Hour'', and ``TeXulous Talk Show''.}
        \item {KXSC Jazz Director tasked with researching, reviewing, and organizing jazz music for the station library.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Instructor} % Job title
    {iD Technology Camps} % Organization
    {Denver, CO} % Location
    {May 2015 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught students age 12-17 programming in C++ and Arduino.}
        \item {Taught students age 6-12 in building simple robots using LEGO Mindstorm kits.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
