%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {CppCon} % Event
    {Real-Time Circuit Simulation with Wave Digital Filters In C++ (Poster)} % Project
    {September 2024} % Date(s)
    {Aurora, CO, USA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Discussed the basic formulation of Wave Digital Filters (WDFs) as a technique for modelling analog circuits.}
        \item {Described the usage of C++ compile-time meta-programming for implementing WDFs.}
        \item {Compared the runtime performance of various WDFs written in C++ and other languages.}
        \item {Presented a simple synthesizer made entirely with WDFs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audio Developer Conference} % Event
    {A Comparison of Virtual Analog Modelling Techniques (Part 2)} % Project
    {November 2023} % Date(s)
    {London, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-presented with Christopher Johann Clarke.}
        \item {Presented a virtual analog model of the Tube Screamer distortion circuit using multiple modelling techniques.}
        \item {Discussed white-box methods: Modified Nodal Analysis, Nodal DK, and Wave Digital Filters with R-Type adaptors.}
        \item {Discussed black-box methods: Recurrent Neural Networks, conditional models, and transformers.}
        \item {Discussed grey-box methods: Symbolic Regression, Differentiable Wave Digital Filters, and Physics-Approximating Neural Networks.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{The Audio Programmer Monthly Meetup} % Event
{Audio Buffers, Buffer Views, and Buffer Iterators} % Project
{Sepember 2023} % Date(s)
{Online} % Location
{
  \begin{cvitems} % Description(s)
    \item {Reviewed data structure design in C++, focusing on owning and non-owning containers.}
    \item {Discussed the design of an ``owning'' audio buffer data structure, and a ``non-owning'' buffer view data structure.}
    \item {Discussed the implementation of custom C++ iterators for audio buffer data structures.}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Northwest C++ Users' Group Meetup} % Event
    {Real-Time Circuit Simulation with Wave Digital Filters} % Project
    {July 2023} % Date(s)
    {Redmond, WA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Discussed the challenges of real-time audio programming.}
        \item {Discussed the basic formulation of Wave Digital Filters (WDFs) as a technique for modelling analog circuits.}
        \item {Described the usage of C++ run-time polymorphism and compile-time meta-programming for implementing WDFs.}
        \item {Demonstrated example applications of WDF models in developing digital audio effects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The Audio Programmer Monthly Meetup} % Event
    {Replacing the AudioProcessorValueTreeState} % Project
    {December 2022} % Date(s)
    {Online} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Discussed the historical and current methods of audio plugin state management with the JUCE framework.}
        \item {Proposed a new approach for managing plugin state with an emphasis on real-time safety.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Acoustical Society of America Annual Meeting} % Event
    {Physical Modelling for Analog Tape Emulation} % Project
    {December 2022} % Date(s)
    {Nashville, USA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Discussed the development of a physical-modelling algorithm for real-time tape emulation.}
        \item {Discussed the physical basis for modelling magnetic hysteresis with nonlinear differential equations.}
        \item {Discussed implementation challenges for real-time tape emulation algorithms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The Audio Programmer Monthly Meetup} % Event
    {Analog Modelling with Wave Digital Filters in C++} % Project
    {December 2021} % Date(s)
    {London, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Discussed the basic formulation of Wave Digital Filters (WDFs) as a technique for modelling analog circuits.}
        \item {Discussed two approaches for implementing WDFs in C++, with trade-offs between flexibility and performance.}
        \item {Demonstrated example applications of WDF models in developing digital audio effects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audio Developer Conference} % Event
    {CI/CD for Audio Plugin Development} % Project
    {November 2021} % Date(s)
    {London, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Discussed the basic concepts and motivations for continuous integration and continuous deployment (CI/CD).}
        \item {Discussed the usefulness of CI/CD for developing audio plugins.}
        \item {Demonstrated several CI/CD workflows in the context of audio plugin development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SARC Virtual Events Series} % Event
    {Creating Audio Effect Plugins for the 21st Century} % Project
    {February 2021} % Date(s)
    {Belfast, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the Sonic Arts Research Centre (SARC) at Queen's University Belfast.}
        \item {Presented a paradigm for developing original and innovative digital audio software.}
        \item {Discussed techniques and philosophies for designing audio software as part of a creative process,
               including signal processing algorithms and user interfaces.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audio Developer Conference} % Event
    {A Comparison of Virtual Analog Modelling Techniques} % Project
    {November 2020} % Date(s)
    {London, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented a virtual analog model of the Klon Centaur guitar pedal
               developed using multiple modelling techniques, including nodal
               analysis, Wave Digital Filters, and Recurrent Neural Networks.}
        \item {An accompanying paper is published on the \href{https://arxiv.org/abs/2009.02833}{ArXiv}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CCRMA DSP Seminar} % Event
    {Complex Nonlinearities for Audio Signal Processing} % Project
    {May 2019} % Date(s)
    {Stanford, CA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the Center for Computer Research in Music and Acoustics (CCRMA) at Stanford University.}
        \item {Presented a series of audio effects constructed from
               innovative uses of nonlinear signal processing techniques.}
        \item {Audio effects presented include harmonic exciters, hysteresis,
               nonlinear filters, subharmonics generators, and more.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {CCRMA DSP Seminar} % Event
    {Exploring Real-Time DSP Systems for Mixing and Performance} % Project
    {Apr. 2019} % Date(s)
    {Stanford, CA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the Center for Computer Research in Music and Acoustics (CCRMA) at Stanford University.}
        \item {Presented overview of previous research and projects to an audience of peers, professors, and the public.}
        \item {Discussed topics including real-time timbral conversion, methods of integrating ``imperfection'' into audio
               DSP systems, and designing user interfaces for DSP systems as an extension of the DSP systems themselves.}
      \end{cvitems}
    }

%---------------------------------------------------------
    % \cventry
    % {CCRMA Open House} % Event
    % {Web Audio Module (WAM) Distortion} % Project
    % {Mar. 2019} % Date(s)
    % {Stanford, CA} % Location
    % {
    %   \begin{cvitems} % Description(s)
    %     \item {Presented a distortion effect originally made in C++, then ported to Web Audio using the Emscripten toolchain.}
    %   \end{cvitems}
    % }

%---------------------------------------------------------
\end{cventries}
