%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founder, Engineer} % Affiliation/role
    {Chowdhury DSP} % Organization/group
    {} % Location
    {June 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed audio plugins including:}
        \begin{itemize}
            \item {ChowTapeModel: An analog tape emulation based on the DAFx-19 paper ``Real-Time Physical Modelling for Analog Tape Machines''.}
            \item {ChowMatrix: A dynamic matrix of stereo delay effects.}
            \item {ChowKick: A kick drum synthesizer based on creative circuit modelling.}
            \item {ChowCentaur: A digital emulation of the Klon Centaur distortion pedal, using Wave Digital Filters and recurrent neural networks.}
            \item {ChowPhaser: A phaser effect based loosely on the Schulte Compact Phasing `A' circuit.}
            % \item {DrumFixer: A plugin that uses modal signal processing to fix drum sounds with unpleasant ``ringing''.}
            % \item {CHOW: A maximally truculent distortion effect.}
            % \item {Chowdhury Distortion: A ``crunchy'' distortion effect with adjustable stereo imperfection.}
        \end{itemize}
        \item {Contributed audio effects and other DSP code to the open-source \href{Surge Synthesizer project}{https://surge-synthesizer.github.io}.}
        \item {Developed modules for the VCV Rack modular synthesis environment.}
        \item {For more information, see the \href{https://chowdsp.com}{Chowdhury DSP website}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer} % Affiliation/role
    {Wave Digital Filters} % Organization/group
    {} % Location
    {Jan. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a minimal C/C++ Library for modelling circuits with Wave Digital Filters (WDFs).}
        \item {Currently includes WDF implementations for basic circuit elements (resistors, capacitors, inductors),
               basic circuit adaptors (series, parallel), and several nonlinear circuit elements.}
        \item {Includes several example WDF models implemented as audio plugins using the JUCE framework,
               as well as a graphical WDF prototyping tool.}
        \item {Ongoing development and documentation can be found on \href{https://github.com/jatinchowdhury18/WaveDigitalFilters}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer} % Affiliation/role
    {audio-dspy} % Organization/group
    {} % Location
    {Oct. 2019 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a Python package for audio signal processing.}
        \item {Currently includes tools for filter design, impulse response manipulation, modal modelling, and nonlinear processing.}
        \item {Development and documentation can be found on \href{https://github.com/jatinchowdhury18/audio_dspy}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Creator} % Affiliation/role
    {NewMixer} % Organization/group
    {} % Location
    {Dec. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A unique digital audio workstation designed to break away from the traditional ``virtual console'' user interface.}
        \item {Individual audio sources are visualized as sound sources in a room; the user can arrange the sources to create a mix with stereo width, and reverberative depth.}
        \item {NewMixer is currently a fully functional mixing tool, supporting saving, exporting, automation, plugin hosting and more.}
        \item {Documentation of NewMixer can be found on \href{https://github.com/jatinchowdhury18/NewMixer}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {DSP Engineer} % Affiliation/role
  %   {Destroy All Circuits} % Organization/group
  %   {} % Location
  %   {June 2019 - June 2020} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Developed DSP models for various effects and characteristics of vintage synthesizers, tape machines, and effects.}
  %       \item {DSP methods include recording and manipulating impulse reponses, circuit modelling, and physical modelling.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Creator} % Affiliation/role
    {The SGUM (Squaminous Geometrically Uncanny Matrix)} % Organization/group
    {Stanford, CA} % Location
    {Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {The SGUM is an expressive standalone drum machine, comprised of nine velocity-sensitive drum pads, with programmable samples and configurations.}
        \item {Designed and built from the SGUM from scratch, including drum pads, circuitry, frame, etc.}
        \item {Programmed firmware for the SGUM, which runs on a Teensy 3.6 microcontroller with an audio shield and uses embedded Faust processing.}
        \item {The entire process was completed in two weeks, and for less than \$100 USD.}
        \item {Documentation for the SGUM can be found on \href{https://www.youtube.com/watch?v=NOcPRS4LxpQ}{YouTube}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Contributor} % Affiliation/role
  %   {Cassettes: A Web Audio Digital Audio Workstation} % Organization/group
  %   {Stanford, CA} % Location
  %   {June 2019 - Sept. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Developed digital audio effects using the Web Audio API and Audio Worklet.}
  %       \item {Effects include:}
  %       \begin{itemize}
  %           \item {Delay: Stereo, Ping-Pong}
  %           \item {Harmonic: Soft-Clipping Distortion, Aural Exciter}
  %           \item {Modulation: Chorus, Flanger}
  %           \item {Dynamics: Limiter, Gate}
  %       \end{itemize}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Co-Founder, Audio Engineer, Technical Advisor} % Affiliation/role
    {NoLava Recording Studios} % Organization/group
    {Los Angeles, CA} % Location
    {Aug. 2017 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Recorded, mixed, and mastered for artists of various styles including acoustic, electronic, rock, country, and punk.}
        \item {Installed, repaired, and maintained speakers, microphones, keyboards, amplifiers, and other studio equipment.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
