%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications \& Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Proceedings of the 22nd International Conference on Digital Audio Effects (DAFx-19)} % Event
    {Real-Time Physical Modelling for Analog Tape Machines} % Project
    {Sept. 2019} % Date(s)
    {Birmingham, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the DAFx-2019 conference.}
        \item {Available on the DAFx Archives: \url{http://www.dafx.de/paper-archive/2019/DAFx2019_paper_3.pdf}.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {The Astrophysical Journal} % Event
    {The CHIME Fast Radio Burst Project: System Overview} % Project
    {Aug. 2018} % Date(s)
    {Vol. 836, No. 1} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-authored with the CHIME/FRB Collaboration}
        \item {Available on the arXiv: \url{https://arxiv.org/abs/1803.11235}.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {CCRMA DSP Seminar} % Event
    {Exploring Real-Time DSP Systems for Mixing and Performance} % Project
    {Apr. 2019} % Date(s)
    {Stanford, CA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented overview of previous research and projects to an audience of peers, professors, and the public.}
        \item {Discussed topics including real-time timbral conversion, methods of integrating ``imperfection'' into audio
               DSP systems, and designing user interfaces for DSP systems as an extension of the DSP systems themselves.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Web Audio Conference 2019} % Event
    {Cassettes - An Online Audio Editor} % Project
    {Dec. 2019} % Date(s)
    {Trondheim, Norway} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Poster session and demonstration by project leader Xingxing Yang
               at WAC-2019.}
        \item {Presented an online audio editor built with the Web Audio API and Audio Worklet.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {CCRMA Open House} % Event
    {Web Audio Module (WAM) Distortion} % Project
    {Mar. 2019} % Date(s)
    {Stanford, CA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented a distortion effect originally made in C++, then ported to Web Audio using the Emscripten toolchain.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
