%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Proc. of the 27th International Conference on Digital Audio Effects} % Event
    {Sample Rate Independent Recurrent Neural Networks for Audio Effects Processing} % Project
    {Sept. 2024} % Date(s)
    {Guildford, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-authored with Alistair Carson, Alec, Wright, Vesa Välimäki, and Stefan Bilbao.}
        \item {Available on the \href{https://www.dafx.de/paper-archive/2024/papers/DAFx24_paper_68.pdf}{DAFx Archives}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Proc. of the Conference on Research in Adaptive and Convergent System} % Event
    {Computationally Efficient Physics Approximating Neural Networks for Highly Nonlinear Maps} % Project
    {Oct. 2022} % Date(s)
    {New York, USA} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-authored with Christopher Johann Clarke and others.}
        \item {Available on the \href{https://dl.acm.org/doi/10.1145/3538641.3561501}{ACM Digital Library}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ArXiv E-Prints: Audio and Speech Processing} % Event
    {chowdsp\_wdf: An Advanced C++ Library for Wave Digital Circuit Modelling} % Project
    {Oct. 2022} % Date(s)
    {Online} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presents a wave digital circuit modelling library with fixed-topology optimizations and other advancements.}
        \item {Available on the \href{https://arxiv.org/abs/2210.12554}{ArXiv}.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {19th Sound and Music Computing Conference} % Event
    {Emulating Diode Circuits with Differentiable Wave Digital Filters} % Project
    {June 2022} % Date(s)
    {Saint Etienne, France} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-authored with Christopher Johann Clarke.}
        \item {Available on \href{https://zenodo.org/record/6566846}{Zenodo}.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Proc. of the 18th Sound and Music Computing Conference} % Event
    {A Wave Digital Filter Modeling Library for the Faust Programming Language} % Project
    {June 2021} % Date(s)
    {Torino, IT} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-authored with Dirk Roosenburg, Eli Stine, and Romain Michon.}
        \item {Available on \href{https://github.com/droosenb/faust-wdf-library/blob/main/SMC-2021-paper/a-wave-digital-filter-modeling-library-for-faust.pdf}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ArXiv E-Prints: Audio and Speech Processing} % Event
    {RTNeural: Fast Neural Inferencing for Real-Time Systems} % Project
    {June 2021} % Date(s)
    {Online} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presents a neural network inferencing library for real-time systems.}
        \item {Available on the \href{https://arxiv.org/pdf/2106.03037.pdf}{ArXiv}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Proc. of the 23rd International Conference on Digital Audio Effects} % Event
    {Water Bottle Synthesis with Modal Signal Processing} % Project
    {Sept. 2020} % Date(s)
    {Vienna, Austria} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the DAFx-2020 conference.}
        \item {Available on the \href{https://www.dafx.de/paper-archive/2020/proceedings/papers/DAFx2020_paper_24.pdf}{DAFx Archives}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Proc. of the 23rd International Conference on Digital Audio Effects} % Event
    {Stable Structures for Nonlinear Biquad Filters} % Project
    {Sept. 2020} % Date(s)
    {Vienna, Austria} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the DAFx-2020 conference.}
        \item {Available on the \href{https://www.dafx.de/paper-archive/2020/proceedings/papers/DAFx2020_paper_3.pdf}{DAFx Archives}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Proc. of the 22nd International Conference on Digital Audio Effects} % Event
    {Real-Time Physical Modelling for Analog Tape Machines} % Project
    {Sept. 2019} % Date(s)
    {Birmingham, UK} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented at the DAFx-2019 conference.}
        \item {Available on the \href{http://www.dafx.de/paper-archive/2019/DAFx2019_paper_3.pdf}{DAFx Archives}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The Astrophysical Journal} % Event
    {The CHIME Fast Radio Burst Project: System Overview} % Project
    {Aug. 2018} % Date(s)
    {Vol. 836, No. 1} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Co-authored with the CHIME/FRB Collaboration}
        \item {Available on the \href{https://arxiv.org/abs/1803.11235}{ArXiv}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Web Audio Conference 2019} % Event
  %   {Cassettes - An Online Audio Editor} % Project
  %   {Dec. 2019} % Date(s)
  %   {Trondheim, Norway} % Location
  %   {
  %     \begin{cvitems} % Description(s)
  %       \item {Poster session and demonstration by project leader Xingxing Yang
  %              at WAC-2019.}
  %       \item {Presented an online audio editor built with the Web Audio API and Audio Worklet.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}

\cvsection{Academic Service}
\begin{cvskills}
  \cvskill
    {Peer Reviewer} % Category
    {Provided peer review for papers submitted to conferences and journals, including
    Audio Mostly 2021, \newline and the EURASIP Journal on Audio, Speech, and Music Processing.}
\end{cvskills}
