%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Researcher} % Affiliation/role
    {Differentiable Wave Digital Filters} % Organization/group
    {} % Location
    {July 2021 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Demonstrated a process for constructing Wave Digital Filter (WDF) circuit models, in conjunction with neural network models of specific circuit elements.}
        \item {Developed a Python library for creating differentiable WDF models, allowing them to be trained via backpropagation.}
        \item {Project documentation is available on \href{https://github.com/jatinchowdhury18/differentiable-wdfs}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Researcher} % Affiliation/role
    {Real-Time Neural Network Inferencing} % Organization/group
    {Stanford, CA} % Location
    {June 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed RTNeural, a C++ library for performing neural inferencing for real-time audio systems.}
        % \item {Developed unit tests to ensure that the library maintains a high level of accuracy.}
        \item {Developed benchmarks to compare the library performance with the PyTorch C++ API.}
        \item {Project documentation is available on \href{https://github.com/jatinchowdhury18/RTNeural}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Researcher} % Affiliation/role
    {Klon Centaur Emulation} % Organization/group
    {Stanford, CA} % Location
    {Mar. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a digital emulation of the Klon Centaur guitar distortion pedal.}
        \item {Used circuit modelling methods including nodal analysis, Wave Digital Filters, and Recurrent Neural Networks.}
        \item {Developed emulation as an audio plugin and guitar pedal using an Arduino Teensy microcontroller.}
        \item {Project documentation is available on \href{https://github.com/jatinchowdhury18/KlonCentaur}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Affiliation/role
    {Modal Waterbottles} % Organization/group
    {Stanford, CA} % Location
    {June 2019 - April 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Worked with a team of researchers to develop acoustical
               models of water bottles using modal signal processing.}
        \item {Developed a real-time water bottle synthesizer using the JUCE framework.}
        \item {Project documentation is available on \href{https://github.com/jatinchowdhury18/modal-waterbottles}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Researcher} % Affiliation/role
    {Complex Nonlinearities} % Organization/group
    {} % Location
    {Aug. 2019 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built frameworks for developing complex nonlinear audio signal processors.}
        \item {Developed a series of open-source plugins to demonstrate the nonlinear frameworks.}
        \item {Published a series of \href{https://medium.com/@jatinchowdhury18/complex-nonlinearities-episode-0-why-4ad9b3eed60f}{Medium articles}
               explaining nonlinear signal processing techniques for a non-technical audience.}
        \item {Project documentation can be found on \href{https://github.com/jatinchowdhury18/ComplexNonlinearities}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Researcher} %Role
    {Bad Circuit Modelling} %Project
    {} %Location
    {Nov. 2019 - June 2020} %Dates
    {
        \begin{cvitems}
              \item{Researched methods for virtual analog circuit modelling
                    to account for imperfections that exist in real-world circuits.}
              \item{Developed simulations and real-time circuit-modelling systems that
                    accurately model the aging and component tolerances of resistors and capacitors.}
              \item{Project documentation can be found on \href{https://github.com/jatinchowdhury18/Bad-Circuit-Modelling}{GitHub}.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Researcher} %Role
    {Analog Tape Modelling} %Project
    {Stanford, CA} %Location
    {Jan. 2019 - Apr. 2019} %Dates
    {
        \begin{cvitems}
              \item{Researched and developed a physical model of an analog, reel-to-reel tape machine.}
              \item{Modelled the nonlinear process of analog tape recording using the Jiles-Atherton model for magnetic hysteresis.}
              \item{Modelled other effects created by analog tape machines, including flutter, playhead loss effects, and biasing effects.}
              \item{Developed an open-source audio plugin implementing the analog tape model as a real-time system.
                    Source code and documentation are available on \href{https://github.com/jatinchowdhury18/AnalogTapeModel}{GitHub}.}
            %   \item{Research began as a class project for Music 420 at Stanford University.}
        \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Lead Researcher} % Affiliation/role
  %   {Non-Uniform Perfect Reconstruction Filterbanks} % Organization/group
  %   {} % Location
  %   {Mar. 2019 - Jun. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Researched and developed a method for real-time filterbank analysis and synthesis, with perfect magnitude reconstruction and linear phase reconstruction.}
  %       \item {Implemented the filterbank in digital audio effect plugins including a Graphic Equalizer and real-time Noise-Supressor.}
  %       \item {Project documentation can found on \href{https://github.com/jatinchowdhury18/NUPR-Filterbanks}{GitHub}.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Research Partner} % Affiliation/role
    {notGuitar} % Organization/group
    {Los Angeles, CA} % Location
    {Jan. 2018 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {notGuitar is real-time timbral conversion system designed to process a guitar input signal to sound like a saxophone.}
        \item {notGuitar was implemented using a Texas Instruments DSK6713 DSP board in May 2018.}
        \item {Documentation for the project can be found on \href{https://github.com/jatinchowdhury18/notGuitar}{GitHub}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
